---
title: 'Assignment 4: Latin Hyper Cube and Sensitivity Analysis'
author: "Sarah Lam & Katheryn Moya & Sofia Urgoiti"
date: "2023-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(purrr)
library(lhs)
library(sensitivity)
library(here)
```


## A. Latin Hypercube Parameter Generation 

Creating a matrix with random samples for the four parameters in our function to choose quantiles that will full sample parameter space. 

```{r}
# Latin Hypercube generation of parameters 
# set a random seed to make things 'random'
set.seed(1)

# which parameters
pnames = c("v", "height", "k_o", "k_d")

# how many parameters
npar =  length(pnames)
# how many samples
nsample = 100

parm_quant = randomLHS(nsample, npar)
colnames(parm_quant)=pnames
# choose distributions for parameters
# v - normally distributed with a mean of 250 cm/s with a standard deviation of 30 cm/s
# height - somewhere between 9.5 and 10.5 m (but any value in that range is equally likely)
# kd and k0 - normally distributed with standard deviation of 1% of their default values
# use random samples to pick the quantiles

parm = as.data.frame(matrix(nrow=nrow(parm_quant), ncol=ncol(parm_quant)))
colnames(parm) = pnames
# for each parameter pick samples 
# I'm using several examples normal distribution (with 10% standard deviation) and uniform with +- 10%
# in reality I should pick distribution from knowledge about uncertainty in parameters

# to make it easy to change set standard deviation / range variation to a variable
pvar = .010

parm[,"v"] = qnorm(parm_quant[,"v"], mean=2.5, sd=0.3) #convert to meters/s for function
parm[,"height"] = qunif(parm_quant[,"height"], min=9.5, max=10.5) 

# normal distribution 1% sd
parm[,"k_d"] = qnorm(parm_quant[,"k_d"], mean=0.7, sd=0.7*pvar)
parm[,"k_o"] = qnorm(parm_quant[,"k_o"], mean=0.1, sd=0.1*pvar)

head(parm) #creating a data frame of 100 potential parameter values based on the mean and sd of each parameter for sensitivity analysis
```

## B. Running Atmospheris Conductance Model 

The model output is atmospheric conductance in mm/s for a given vegetation type (forest). 

```{r}
source(here("R/Catm.R"))

catm <-  parm %>% pmap(Catm)

head(catm)

#turn results into a data fram 

catm_df <- do.call("rbind", catm) 

catm_parm <- cbind(parm, catm_df)

nrow(catm_df)
```

## C. Plotting Conductance Estimates & Parameter Uncertainty

```{r}
#Sarah
# density of boxplot to visualize all of the output
# 1 plot
```


## D. Plotting Conductance Against Each Parameter
```{r}
#Sofia
# plotted against the parameter 
# four plots 
```


## E. Partial Rank Correlation Coefficients
```{r}
#Katheryn

```


## F. Discussion


